---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# QTE.RD

<!-- badges: start -->
<!-- badges: end -->

The goal of **QTE.RD** is to provide comprehensive tools for testing, estimating, and conducting uniform inference on quantile treatment effects (QTEs) in sharp regression discontinuity (RD) designs. When treatment effects vary across covariate-groups, QTE.RD facilitates the estimation, testing, and visualization of heterogeneous effects by incorporating covariates and applying the robust bias correction methods developed by Qu, Yoon, and Perron (2024, doi:10.1162/rest_a_01168).

The package is available on CRAN and can be loaded by

```{r}
library(QTE.RD)
```

## Example

The following example demonstrates how to use the `rd.qte` function from the **QTE.RD** package, using data from Duflo, Dupas, and Kremer (2011, AER). It estimates the quantile treatment effects of tracking on student achievement.

```{r example, result="hide"}
data("ddk_2011")
trk <- ddk_2011$tracking
high <- 1-ddk_2011$lowstream
ts <- ddk_2011$totalscore
yy <- (ts - mean(ts[trk==0],na.rm=T))/sd(ts[trk==0],na.rm=T)
xx <- ddk_2011$percentile
yc <- yy[trk==1]
xc <- xx[trk==1]
dc <- high[trk==1]

A <- rd.qte(y=yc,x=xc,d=dc,x0=50,z0=NULL,tau=(1:9/10),bdw=20,cov=0,bias=1)
summary(A,alpha=0.1)
```
